%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% jj
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
% \usepackage[colorinlistoftodos]{todonotes}
\usepackage{algorithmic}
\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
\usepackage{multirow}
\usepackage{tablefootnote}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{flushend}
\usepackage{color}
\usepackage{enumitem}
\usepackage{array, makecell}
\usepackage{footmisc}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{ulem} 
\usepackage{xcolor}
\newcommand\yang[1]{\textcolor{magenta}{[Hongxia: #1]}}
\newcommand\blue[1]{\textcolor{blue}{#1}}
\newcommand\red[1]{\textcolor{blue}{#1}}
\newcommand\zc[1]{\textcolor{blue}{[zc: #1]}}
\newcommand\xz[1]{\textcolor{teal}{[xz: #1]}}
% \newcommand\hide[1]{}
\newcommand\green[1]{\textcolor{green}{#1}}
\newcommand{\hide}[1]{}
\newcommand{\jie}[1]{\textbf{\color{red}[(JT: #1 )]}}  % to fix
\newcommand{\vpara}[1]{\vspace{0.07in}\noindent\textbf{#1 }}
\newcommand{\model}{{ComiRec}}

\newtheorem{definition}{Definition}
\newtheorem{problem}{Problem}


%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.

\copyrightyear{2020}
\acmYear{2020}
\setcopyright{acmcopyright}
\acmConference[KDD '20]{Proceedings of the 26th ACM SIGKDD Conference on Knowledge Discovery and Data Mining}{August 23--27, 2020}{Virtual Event, CA, USA}
\acmBooktitle{Proceedings of the 26th ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD '20), August 23--27, 2020, Virtual Event, CA, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3394486.3403344}
\acmISBN{978-1-4503-7998-4/20/08}

%% These commands are for a PROCEEDINGS abstract or paper.

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\settopmatter{printacmref=true}

\begin{document}

\fancyhead{}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Controllable Multi-Interest Framework for Recommendation}
% \title{Controllable Multi-Interest Sequential Recommendation}

\author[Y. Cen, J. Zhang, X. Zou, C. Zhou, H. Yang and J. Tang]{
    Yukuo Cen$^{\dagger}$, Jianwei Zhang$^{\ddagger}$, Xu Zou$^{\dagger}$, Chang Zhou$^{\ddagger}$, Hongxia Yang$^{\ddagger*}$, Jie Tang$^{\dagger*}$
}
\affiliation{
    $^\dagger$ Department of Computer Science and Technology, Tsinghua University
}
\affiliation{
    $^\ddagger$ DAMO Academy, Alibaba Group
}
\email{
  {cyk18, zoux18}@mails.tsinghua.edu.cn
}
\email{
  {zhangjianwei.zjw, ericzhou.zc, yang.yhx}@alibaba-inc.com
}
\email{
  jietang@tsinghua.edu.cn
}


%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\authors}{Yukuo Cen, Jianwei Zhang, Xu Zou, Chang Zhou, Hongxia Yang and Jie Tang}
\renewcommand{\shortauthors}{Y. Cen et al.}


%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[1]{Hongxia Yang and Jie Tang are the corresponding authors.}
\renewcommand{\thefootnote}{\arabic{footnote}}

Recently, neural networks have been widely used in e-commerce recommender systems, owing to the rapid development of deep learning. 
We formalize the recommender system as a sequential recommendation problem, intending to predict the next items that the user might be interacted with. 
Recent works usually give an overall embedding from a user's behavior sequence. However, a unified user embedding cannot reflect the user's multiple interests during a period. 
In this paper, we propose a novel \textbf{\textit{co}}ntrollable \textbf{\textit{m}}ulti-\textbf{\textit{i}}nterest framework for the sequential \textbf{\textit{rec}}ommendation, called \model. Our multi-interest module captures multiple interests from user behavior sequences, which can be exploited for retrieving candidate items from the large-scale item pool. These items are then fed into an aggregation module to obtain the overall recommendation. The aggregation module leverages a controllable factor to balance the recommendation accuracy and diversity. 
We conduct experiments for the sequential recommendation on two real-world datasets, Amazon and Taobao. Experimental results demonstrate that our framework achieves significant improvements over state-of-the-art models\footnote{Code is available at \url{https://github.com/THUDM/ComiRec}}. 
Our framework has also been successfully deployed on the offline Alibaba distributed cloud platform. %Results on the billion-scale industrial dataset further confirm the effectiveness and efficiency of CapsRec in practice.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003317.10003347.10003350</concept_id>
<concept_desc>Information systems~Recommender systems</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010257.10010293.10010294</concept_id>
<concept_desc>Computing methodologies~Neural networks</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Recommender systems}
\ccsdesc[500]{Computing methodologies~Neural networks}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{recommender system; sequential recommendation; multi-interest framework}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}\label{sec:intro}
\input{1.intro}

\section{Related Work} \label{sec:related}
\input{2.related}

\section{Methodology}\label{sec:model}
\input{3.model}

\section{Experiments}\label{sec:exp}
\input{4.exp}

\section{Conclusion} \label{sec:conclusion}
\input{5.conclusion}



%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
The work is supported by the
NSFC for Distinguished Young Scholar 
%jie tang
(61825602),
%chunyuan zhou
NSFC (61836013), 
and a research fund supported by Alibaba Group.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

%%
%% If your work has an appendix, this is the place to put it.
\appendix
\section{Appendix}
\label{sec:appendix}
\input{6.appendix}


\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.
